%-------------------------
% Resume in Latex
% Author : Kunj Shah
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.475in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\medium{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kunj Shah} & Email : \href{mailto:kunjshah45@gmail.com}{kunjshah45@gmail.com}\\
  \textit{}{9830 Reseda Blvd, Los Angeles, CA 91324} & {Mobile : +1 7472066201}\\
  \textit{} & {
  
  \href{https://www.linkedin.com/in/kunjshah45}{https://www.linkedin.com/in/kunjshah45}}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University, Northridge }{Northridge, Los Angeles, USA}
      {Masters in Computer Science }{Aug. 2021 - Current}
    \resumeSubheading
      {MIT Art, Design and Technology School of Engineering }{Pune, India}
      {Bachelor in Computer Science;  GPA: 7.19 }{Aug. 2017 - June 2020}
    \resumeSubheading
      {SVKM's Shri Bhagubhai Mafatlal Polytechnic}{Mumbai, India}
      {Diploma in Computer Science Engineering; Percentage 82 }{Aug. 2014 - July. 2017}
  \resumeSubHeadingListEnd


%-----------Career Objective-----------------
\section{Career Objective}
        \resumeItem{}
        {Always ready to take up challenges and learn about the latest trends. Being part of progressive organization that gives a scope to enhance my knowledge and utilizing my skills towards the growth of the organization and personal skills.}
        % Machine Learning practitioner.
          
        \resumeItemListEnd

%-----------EXPERIENCE-----------------
\section{Technical Experience}
  \resumeSubHeadingListStart
            \resumeItem{Software Developer - Expertrons [December, 2020 - May, 2021] }{}
            \resumeItemListStart{}
                \resumeItem{}
                  {Worked on Mobile Application using React Native, Redux Saga, React and Nodejs for backend}
                \resumeItem{}
                  {Also worked with MongoDB and made scripts for automating tasks. Actively involved in setting up AWS and migration and on-premise Sentry. }
            \resumeItemListEnd
            \resumeItem{Backend Intern - GeekWork [December,2019 - March, 2020] }{}
            \resumeItemListStart{}
                \resumeItem{}
                  {Worked on ROS, Contributed in developing movement of AGV, collision avoidance.}
                \resumeItem{}
                    {Integrated API's such as Onedrive, Google Drive, Slack for client.}
                \resumeItem{}
                    {Learned fetching data and files from clouds, process it through Tika before storing it in Elastic Search.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Projects}
  \resumeSubHeadingListStart
        \resumeItem{Nibodh - Portal for searching schools [Flask Micro-Framework, MongoDb Database] (March, 2020 – May, 2020)}
            { Platform where parents can to search best fit for their children. Become proficient in Flask, MongoDB. Indexing is implemented for quick results while searching schools. }
            
        \resumeItem{Automated Guided Vehicle [ROS, Flask Micro-Framework, MySQL Database] (January, 2020 – March 2020)}
            {Industrial Automated guided vehicle build on ROS and python for industrial operations. Gained knowledge about ROS fundamentals, publisher - subscriber model, sockets. }
       
        \resumeItem{College Fest Events [Android Studio, MongoDB, Flask Micro-Framework]: (January, 2019)}
          {Students can register for events in Persona Fest 2019, received notification update about events. Java for android app, with Flask handling the admin panel for various operations.}
        
        % \resumeItem{Seat booking Portal [Django Framework, MySQL Database]: (2018, June - 2018, August)}
        %   {College Auditorium portal. Admin can post event and it will be visible to all the students. Students on the other hand can view the event and book their seat for events and download the ticket in PDF format. Python's Django Framework is used for creating the web. I acquired knowledge about Django's fundamentals and features}
        
        \resumeItem{Billing Software(GST) [PHP, MySQL Database] (March, 2016 - July, 2017).}
          {Billing software handles stock management, Bill generation, CRM, adding products, taking backups, notifying for the overdue bills, giving statics, generation of bills, etc. }
          
      \resumeItemListEnd



%-----------Skills-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{}
      {C++, Python, Django, Flask, Nodejs, React Native, MySQL, MongoDB.}
    \resumeSubItem{}
      {Worked With:ROS, Android Studio, Arduino Board, Web Development, AJAX, JQUERY}
  \resumeSubHeadingListEnd
  
 %--------------Extracurricular activities--------------
\section{Extracurricular activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Open source Contribution :}
        \resumeItemListStart
            \resumeItem{}
                {india-location-details - NPM package to find details of Indian regions by Pincode, City, State.}
        \resumeItemListEnd
    \resumeSubItem{Participated :}{ Winner HAB59 by MIT ADT, 1st runner up Codefest's Haxplore by IIT-BHU, 2nd runner up AISSMS hackathon, 2nd runner up KJSCE HACK, Rajasthan 5.0, iHack}
    \resumeSubItem{Certification Courses :}{MongoDB, Devops}
  \resumeSubHeadingListEnd
  

%--------------Volunteer Work--------------
\section{Volunteer work}
  \resumeSubHeadingListStart
    \resumeSubItem{}{Organizer of Code Break 1.0, Hosted on Devfolio.}
    \resumeSubItem{}{Student Organizer of all CSE-IT events held in Persona Fest 2019.}
    \resumeSubItem{}{Student Head of Sponsorship team for Persona Fest 2018.}
  \resumeSubHeadingListEnd
  
% %--------------Social media--------------
% \section{Social Accounts}
%   \resumeSubHeadingListStart
%     \resumeSubItem{}{LinkedIn - https://www.linkedin.com/in/kunjshah45/}
%     \resumeSubItem{}{Github - https://github.com/kunjshah45}
%   \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
